Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Edit introduction.
Several paragraphs were cut for brevity.

Mechanical vapor compression has been the dominant cooling technology for the past century \cite{bib:nik} but, despite its dominance, it still faces an increasing number of challenges related to the its environmental footprint. The large entropy generation associated with vapor compression processes makes this techonology constrained by low exergy efficiencies, in particular for compact systems \cite{KITANOVSKI2015288}. In addition, the phase-out of refrigerants \textcolor{black}{with} ozone depleting \textcolor{black}{and global warming potentials has} introduced the use of flammable substances, with their own set of risks for consumer applications \cite{bib:iir-flammable} and technologial challenges \cite{bib:lionte18-adapt}.

The term \emph{caloric cooling} is \textcolor{black}{generally} applied to alternative cooling techonologies in which the cooling effect is generated by the response of a solid material to a physical \textcolor{black}{stimulus}. The absence of hazardous gases, compressors \textcolor{black}{and throttling devices} makes these technologies potentially more efficient, \textcolor{black}{scalable}, silent and environmentally friendly. Magnetic refrigeration (MR) is the most advanced of all caloric technologies \cite{KITANOVSKI2015288}; in particular, with the classes of magnetic refrigerants currently available, magnetocaloric refrigeration seems promising for applications in small temperature span (around \SI{20}{\kelvin}), such as winecoolers \textcolor{black}{and air conditioners} \cite{KITANOVSKI2015288}.

\nomenclature[vm]{MR}{Magnetic (or Magnetocaloric) Refrigeration}

In magnetic refrigeration, a \emph{magnetocaloric material} (MCM) \textcolor{black}{is subjected to a cyclical change of the applied} magnetic field, and its temperature \textcolor{black}{changes as a result} of the \emph{magnetocaloric effect} (MCE). The magnitude of the MCE  \textcolor{black}{depends} on  parameters \textcolor{black}{related to} characteristics of the material, magnetic field variation and temperature, and its maximal at the transition Curie temperature of the material. For a thorough introduction to the magnetocaloric effect and magnetocaloric materials, the reader is referred to \cite{bib:smith-magneto}.

\nomenclature[vm]{MCM}{Magnetocaloric Material}

For operating conditions typical of a low-temperature span magnetic refrigerator, the MCE is typically \textcolor{black}{on} the order of \num{2}-\SI{5}{\kelvin}. \textcolor{black}{T}o amplify this \textcolor{black}{temperature change}, heat regeneration is usually employed \cite{bib:kitanovski}. Active magnetic regenerators (AMR) are thermal devices where the magnetocaloric material constitutes a solid matrix through which flows an aqueous heat transfer fluid, and is cyclically magnetized and demagnetized to activate the magnetocaloric effect.  \textcolor{black}{A regenerator is essentially a cascade of infinitesimal ``layers'' of MCM that are activated simultaneously} to build up a temperature profile \textcolor{black}{along its length}. These layers can be made of the same material, yielding an homogeneous regenerator; however, given the  dependence  of the MCE with temperature, it is an interesting strategy to build \emph{multilayer} regenerators, where each layer is composed of a different material \textcolor{black}{that} will work around its \textcolor{black}{own} Curie temperature, maximizing the magnetocaloric effect of each portion.

@@

The five main subsystems in an AMR-based magnetic refrigerator can be identified as follows \cite{bib:jaime,bib:trevizoli16_pump}:

\begin{enumerate}
\item magnetic circuit; \label{item:1}
\item active magnetic regenerator; \label{item:2}
\item flow management system; \label{item:3}
\item control system; \label{item:4}
\item transmission system; \label{item:5}
\item heat exchangers and cabinet. \label{item:6a}
\end{enumerate}

The magnetic circuit generates oscillating magnetic fields that activate the MCE \textcolor{black}{in} the active magnetic regenerators. As previously explained, the regenerators are composed of magnetocaloric porous media, and the flow management system provides the alternating fluid flow through the beds. The control system \textcolor{black}{serves} the purpose of synchronizing the fluid flow regime with the magnetic field variations. Finally, the heat exchangers are responsible for transferring the cooling effect from the AMR to the refrigerated cabinet and the rejected heat to the surroundings.

@@

Among the challenges cited in the literature for further improvement of magnetic refrigerators, two can be highlighted \cite{bib:eriksen16_activ}:

\begin{enumerate}
\item Better use of AMR and magnetic circuit models during the design process, to identify optimal geometric and operating parameter;
\item Better study of losses that are present in a magnetic cooling device.
\end{enumerate}

\textcolor{black}{In} other words, these challenges arise due to \emph{interactions} between different subsystems \textcolor{black}of a magnetic refrigerator. In these context, the focus on the aforementioned waveforms is a suitable approach for optimizing the performance of magnetic refrigerators, as these profiles represent interactions between systems. As it will be seen, mathematical models for AMRs take these waveforms as input, and they are generated by models for other components.

@@

In this work, we focus on magnetic profiles, which are less studied in the literature. The studied waveforms are depicted in \autoref{fig:profiles}, identified by the transitions between states. The instantaneous profile represents step-like changes between high and low levels of the magnetic field, while the ramp profile has linear variations between these states. The rectified cosine profile is a common waveform found in the literature that has a continuous variation of the applied magnetic field.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=8cm]{profiles_all}
  \caption{Magnetic profiles studied in this paper}
  \label{fig:profiles}
\end{figure}

The instantaneous magnetic profile is characteristic of the Brayton AMR cycle, where the magnetization and demagnetization steps must be done adiabatically, as shown in \autoref{fig:brayton}; compared to other common cycles such as the Ericsson, the Brayton cycle results in the highest cooling capacities for the same operating  parameters \cite{bib:kitanovski}, at the expense of lower coefficient of performance.

\begin{figure}[!ht]
  \centering

  \caption{Brayton AMR cycle}
  \label{fig:brayton}
\end{figure}

 In practice, the ramp profile is a more feasible realization with finite transition times, and its synchronization with the fluid flow profile can yield different performance levels \cite{TUSEK20111507}. In particular, the plateaus of magnetic field should be centered with the blow durations \cite{bib:bjoerk11_amr}.
\autoref{fig:sync} shows the syncronization schema between the magnetic and fluid flow profiles, showing the ramp magnetic profile as an example.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=8cm]{profiles_rm_and_flow_instantaneous}
  \caption{Ramp magnetic profile (solid lines) and instantaneous fluid flow profile (dashed lines)}
  \label{fig:sync}
\end{figure}

This paper uses the AMR model developed by \cite{bib:trevizoli16_perfor_model}, and the same authors had studied magnetic profiles waveforms in an earlier work \cite{bib:asme-mce}. However, their amplitudes was not varied, nor were they investigated with different geometries.

The present works combines the gaps from the above cited papers in investigating the performance of a magnetic refrigerator under different magnetic profile waveforms. These waveforms are mathematically modeled, and the cooling capacity and coefficient of performance are calculated based on the profiles parameters, while also investigated how the AMR geometry affect the performance in combinations with the magnetic profile. The fluid flow profile is assumed fixed in shape, although its parameters are also variied. The emulate constraints on an operating point of actual magnetic refrigeration devices, the temperature span is set fixed, and hence few comments are made on second-law efficiency.

>>>>

Mechanical vapor compression has been the dominant cooling technology for the past century \cite{bib:nik} but, despite its dominance, it still faces an increasing number of challenges related to the its environmental footprint. In particular, the phase-out of refrigerants \textcolor{black}{with} ozone depleting \textcolor{black}{and global warming potentials has} introduced the use of flammable substances, with their own set of risks for consumer applications \cite{bib:iir-flammable} and technological challenges \cite{bib:lionte18-adapt}.

Magnetic refrigeration (MR) is an advanced cooling technology with no use of hazarduous gases, where a \emph{magnetocaloric material} (MCM) \textcolor{black}{is subjected to a cyclical change of the applied} magnetic field, and its temperature \textcolor{black}{changes as a result} of the \emph{magnetocaloric effect} (MCE). The magnitude of the MCE  \textcolor{black}{depends} on  material parameters, magnetic field variation and temperature, and its maximal at the Curie temperature of the material. For a thorough introduction to the magnetocaloric effect and magnetocaloric materials, the reader is referred to \cite{bib:smith-magneto}.

\nomenclature[vm]{MR}{Magnetic (or Magnetocaloric) Refrigeration}
\nomenclature[vm]{MCM}{Magnetocaloric Material}
\nomenclature[vm]{MCE}{Magnetocaloric Effect}

For operating conditions typical of a low-temperature span magnetic refrigerator, the MCE is typically \textcolor{black}{on} the order of \num{2}-\SI{5}{\kelvin}. \textcolor{black}{T}o amplify this \textcolor{black}{temperature change}, heat regeneration is usually employed \cite{bib:kitanovski}. Active magnetic regenerators (AMR) are thermal devices where the magnetocaloric material constitutes a solid matrix through which flows an aqueous heat transfer fluid, and which is cyclically magnetized and demagnetized to activate the magnetocaloric effect.  \textcolor{black}{Such a regenerator is essentially a cascade of infinitesimal ``layers'' of MCM that are activated simultaneously} to build up a temperature profile \textcolor{black}{along its length}. These layers can be made of the same material, yielding an homogeneous regenerator; however, given the  dependence  of the MCE with temperature, it is an interesting strategy to build \emph{multilayer} regenerators, where each layer is composed of a different material \textcolor{black}{that} will work around its \textcolor{black}{own} Curie temperature, maximizing the magnetocaloric effect of each portion.

@@

@@

@@

In this work, we focus on magnetic profiles, which are less studied in the literature.
These waveforms are usually investigated in terms of their synchronization with the fluid flow profile \cite{TUSEK20111507,bib:bjoerk11_amr}. This paper uses the AMR model developed by \cite{bib:trevizoli16_perfor_model}, and the same authors had studied magnetic profiles waveforms in an earlier work \cite{bib:asme-mce}. However, their amplitudes was not varied, nor were they investigated with different geometries.

The present work combines the gaps from the above cited papers in investigating the performance of a magnetic refrigerator under different magnetic profile waveforms. These waveforms are mathematically modeled, and the cooling capacity and coefficient of performance are calculated based on the profiles parameters, while also investigated how the AMR geometry affect the performance in combinations with the magnetic profile. The fluid flow profile is assumed fixed in shape, although its parameters are also varied. To emulate constraints on an operating point of actual magnetic refrigeration devices, the temperature span is set fixed, and hence few comments are made on second-law efficiency.
